\chapter{previous work}
\section{Computer Vision}

Computer vision is a very high interest field with a diverse range of applications.  Computer vision primarily has to do with converting a visual input into something the computer can ``understand'' and then perform a specific action based on that observation.  A good example is red-light cameras, if the computer vision system detects what it believes to be someone running the red light, it snaps a picture, records some video as record for a law enforcement officer to evaluate.

Additionally commercial license plate readers have become available.  A license plate scanner takes a still image of a vehicle, then detects the license plate and then ``reads'' the numbers on the license plate of that vehicle.


\section{Optical Character recognition}

Optical Character Recognition is perhapse the most heavily explored area of computer vision.  Specifically, OCR has to do with a computer taking in a digital image, and outputing a text representation of what the computer believes it represents.  OCR systems have been in existance since the 60's and continue to make improvements over time.

The USPS began using OCR systems for automated letter sorting in 19??. 

\section{Document Understanding}

Document Understanding includes OCR, but also includes additional data such as layout and document type.  For example, a Book or Technical Report has a much different layout and organization than a Newspaper or Magazine.  Systems which correctly interpret the organization of a document can produce a more accurate digital representation of said document.  This reduces the labor requirement for digitizing large amounts of printed material, and makes the scanned material more available and discoverable.

\section{Historical Document Understanding}

Computer systems which process historical images face special problems such as degredation of the artifact over time.  There also exists a great variet


\section{Available collections of documents}

Several measeums have digitized thier collections and posted these collections on the Internet.

Digital Public Library:
Metropolitan Measeum of Art:
CADAL & the million book project:

\section{available collections of Chinese Calligraphy}

Metropolitan Meauseum of artifact
Seattle Meusium of Art History, Or something I think.
CADAL Million book Project,
Also, CADAL Calligraphy project.



